Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
related works

%%Bayesian inference is a standard tool for data analysis which is
%% also a building block of probabilistic programming languages
Many statistical applications are driven by Bayesian inference.
This is a standard statistical tool in which a prior distribution is combined
with a sample of observed data in order to estimate a new posterior distribution.
%is a standard statistical tool that is useful to
%estimate a posterior distribution when a prior distribution is given
%and some data is observed.

@@

%%we consider bayesian inference with posterior perturbation 
%%which could be used as a plug and play in PPL citing CCS2016
In this work we consider the design space of  parametric Bayesian
inference mechanisms guaranteeing differential privacy. Our work is
motivated by recent developments in the area of probabilistic
programming where several tools have been proposed to perform
parametric and non-parametric Bayesian inference in an efficient
way.

@@

\noindent \textbf{Main contributions.}
What follows is a summary of the main contributions of this work.
\begin{itemize}
	\item We give a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
   %    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
	\item We propose two ways of improving the accuracy of this basic mechanism: 1) We calibrate noise to a measure of sensitivity determined by a metric between distributions
      (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) We scale noise according to a a smooth upper bound on the local sensitivity, rather than according to global sensitivity.
  \item We implement the new proposed mechanism and other art-of-state mechanisms, comparing their performances in terms of accuracy and privacy.
\end{itemize}

@@

A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.

In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \cite{dimitrakakis2014robust,zhang2016differential,zheng2015differential,wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new. moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism. That's why we explore different metrics and different algorithms over the design space.

>>>>

%%Bayesian inference is a standard tool for data analysis which is
%% also a building block of probabilistic programming languages
Many statistical applications are driven by Bayesian inference.
This is a standard statistical tool in which a prior distribution is combined
with a sample of observed data in order to estimate a new posterior distribution.

%is a standard statistical tool that is useful to
%estimate a posterior distribution when a prior distribution is given
%and some data is observed.

@@

%%we consider bayesian inference with posterior perturbation 
%%which could be used as a plug and play in PPL citing CCS2016

In this work we consider the design space of  parametric Bayesian
inference mechanisms guaranteeing differential privacy. Our work is
motivated by recent developments in the area of probabilistic
programming where several tools have been proposed to perform
parametric and non-parametric Bayesian inference in an efficient
way.

@@

%\noindent \textbf{Main contributions.}
In summary, the main contributions of our work are:
\begin{itemize}
	\item We give a new differentially private Bayesian inference mechanism based on the standard exponential mechanism.
   %    \item A full proof of $(\epsilon, \delta)$-differential privacy of the mechanism is given in the paper. 
	\item We propose two ways of improving the accuracy of this basic mechanism: 1) We calibrate noise to a measure of sensitivity determined by a metric between distributions
      (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) We scale noise according to a a smooth upper bound on the local sensitivity, rather than according to global sensitivity.
  \item We implement the new proposed mechanism and other art-of-state mechanisms, comparing their performances in terms of accuracy and privacy.
\end{itemize}

@@

% A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.

Several works have considered the intersection of Bayesian Inference and differential
privacy. \citet{williams2010probabilistic} explored the use of
probabilistic inference to improve the accuracy of differentially
private data analyses. A similar approach has been also studied by
\citet{xiao2012bayesian}.

A general trend has been to study robustness conditions
for different likelihood functions and different classes of conjugate priors 
guaranteeing differential privacy for samples taken from a
posterior distribution. \citet{dimitrakakis2014robust}
consider this approach and identify some general robustness technique
which can be applied to several models including the one considered in
this paper. Similarly, \citet{zheng2015differential} considers a similar approach
but with different conditions. \citet{zhang2016differential} extend
the previous approaches to address more general models with multiple
random variables. 
\citet{wang2015privacy} identifies
conditions guaranteeing differential privacy for samples generated
using standard montecarlo algorithm.
\citet{GeumlekSC17} consider the problem of releasing samples from
distributions in the exponential family under the constraints imposed
by Renyi differential privacy. 
\citet{Zhang2017privbayes} propose a technique for releasing high
dimensional data based on the differentially private learning of a
Bayesian graphical model.

Few works take an approach similar to the one we consider here. 
\citet{dimitrakakis2015differential} study differentially private
posterior release by output perturbation based on Laplace noise for the Beta-Binomial
model. However, they measure accuracy in terms of $\ell_1$
distance over the parameters and in term of KL-divergence over the distribution.  \citet{foulds2016theory}
generalizes the approach of \citet{dimitrakakis2015differential} by
analyzing further the impact that Laplace noise has on the inference.
They also focus on accuracy measured in term of  $\ell_1$ distance
over the parameters. \citet{BartheFGAGHS16} study a verification
method for probabilistic programs including constructs for Bayesian
inference. In their work they also study an approach based on the use
of the exponential mechanism with the Hellinger distance as scoring
function. We show here that their approach achieve very poor utility.

% 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new. moreover, their design spaces are more specific to the $\ell_1$ norm and Laplace mechanism. That's why we explore different metrics and different algorithms over the design space.
